---
output: 
  word_document:
    reference_docx: "packet_styles.docx"
---

```{r setup, include = FALSE}
library(tidyverse)
library(lubridate)
library(googlesheets4)
library(RefManageR)
library(activityReporteR)
library(flextable)

report_start_date <- as.Date("2020-05-01")
report_end_date <- as.Date("2100-01-01")

data_gs_url <- "https://docs.google.com/spreadsheets/d/11XRsF-MupYcnZlykUe6YHAGe1A16CxJyq9nT3oSbDeg/edit#gid=0"
gs4_auth("haoye@ufl.edu")

data_bib_file <- "my_lib.bib"
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           cite.style = "apa",
           style = "markdown",
           max.names = Inf, 
           hyperlink = FALSE,
           dashed = FALSE, 
           use.misc.default.format = TRUE)
my_bib <- ReadBib(data_bib_file, check = FALSE)

dept_name <- "Academic Research Consulting & Services"

set_flextable_defaults(
    font.family = "Times New Roman", 
    font.size = 11, 
    border.color = "black", 
    table.layout = "fixed", 
    padding.top = 3, padding.bottom = 1
)

source("R/download_gs_data.R")
source("R/format_data.R")
source("R/format_word_tables.R")
source("R/print_data.R")

knitr::opts_chunk$set(echo = FALSE, results = "asis")
```

```{r check data sources}
data_files <- c("data/degrees.RDS", 
                "data/jobs.RDS", 
                "data/effort_perc.RDS", 
                "data/teaching_summary.RDS", 
                "data/teaching_evals.RDS", 
                "data/grad_committees.RDS",
                "data/teaching.RDS", 
                "data/research.RDS",
                "data/videos.RDS", 
                "data/grants.RDS", 
                "data/service.RDS", 
                "data/reviews.RDS", 
                "data/awards.RDS", 
                "data/talks.RDS")
data_files_found <- file.exists(here::here(data_files))
if (!all(data_files_found))
{
    missing_files <- paste0("file '", 
                            data_files[!data_files_found], 
                            "' not found")
    vapply(missing_files, warning, "", call. = FALSE)
}
```

# NOMINEE INFORMATION COVER SHEET 

<!--

The cover sheet automatically gets added after the PDF is uploaded into UF's OPT system.
-->

# BRIEF DESCRIPTION OF JOB DUTIES 

<!-- Briefly describe your assigned duties and responsibilities. Provide context for these responsibilities (ie. the relevance and importance to your discipline and UF -->
<!-- Describe the duties of your position – this is not really the place for first person input (instead of ‘I do this and I do that’, it should be a description of the duties). Take advantage of this opportunity to ‘translate’ your work for reviewers who are unfamiliar with librarianship. -->

<!-- MRT: I split the first sentence into 2 because it was pretty long, and most people won’t be familiar with what you do so important to make it easy for them. I’d be real obvious about how ARCS serves the whole campus, and that ARCS is Smathers Libraries -->

<!-- As the reproducibility librarian, I am responsible for developing and executing on an institutional strategy for education and support of trans-disciplinary research reproducibility and open science for the University of Florida community. These responsibilities include programming for and support of information retrieval/storage, data- and computational workflows, responsible conduct of research, and open scholarship broadly defined (e.g., open access, publishing data and code, preprints). I serve as the liaison librarian to several departments and programs in the College of Medicine and College of Public Health and Health Professions: Biostatistics, Health Outcomes and Biomedical Informatics, and the Graduate Program in Biomedical Sciences. My position provides interdisciplinary information consultation services in a variety of modes, designs workshops to promote research reproducibility, performs course-integrated instruction, and participates in the Smathers Libraries' teaching initiatives. In addition, I support special projects and programs related to the overall mission of the Academic Research Consulting & Services department, including coordinating and promoting programs and services, such as the Student HiPerGator Sponsorship program. I serve on and lead committees within UF, and for national and international professional organizations, when such responsibilities complement or directly relate to promoting research reproducibility. My scholarship explores new modes and models for open research broadly and possible interventions to shift existing practices, such as through instruction, technical infrastructure, and sociocultural incentives. -->

The reproducibility librarian is responsible for developing and executing on a strategy for trans-disciplinary research reproducibility and open science for the University of Florida community. These topics span a variety of research practices, including information retrieval/storage, data- and computational workflows, responsible conduct of research, and open scholarship broadly defined (e.g., open access, publishing data and code, preprints). This position also serves as the liaison librarian to several departments and programs in the College of Medicine and College of Public Health and Health Professions: Biostatistics, Health Outcomes and Biomedical Informatics, and the Graduate Program in Biomedical Sciences.
Activities of the reproducibility librarian include information consultation services in a variety of modes, the design and teaching of workshops in research reproducibility, course-integrated instruction, and participation in broader teaching initiatives in the Smathers Libraries.
The position additionally supports special projects and programs related to the overall mission of the Academic Research Consulting & Services department, including the Student HiPerGator Sponsorship program, Artificial Intelligence, and Research Integrity.
The reproducibility librarian is expected to engage in impactful and innovative scholarship. My research specifically explores new modes and models for open research broadly and possible interventions to shift existing practices, such as through instruction, technical infrastructure, and sociocultural incentives.
As faculty of a leading public university, the reproducibility librarian engages in service and leadership for internal committees and for various national and international professional organizations, especially when such responsibilities complement or directly relate to promoting research reproducibility. 

## Impact of COVID pandemic on Job Duties
<!-- In this optional section faculty may provide a statement regarding the impact of the COVID-19 pandemic on the nominee’s professional life -- up to 500 words. This statement should explain how the nominee adjusted/compensated for pandemic-related difficulties impacting their research, teaching, clinics, extension or service. Please see http://aa.ufl.edu/policies/tenure-and-promotion-information/ for more details. This was a new section beginning in 2021. -->

<!-- MRT: I’d probably add something here about how long the libraries were closed to in-person. -->


The COVID pandemic had a substantial and indeterminate effect on my professional responsibilities. In between my hire and my start in May 2020, the university closed, without a specific plan for re-opening. On top of the challenges of starting a new position, there were many obstacles resulting from operating in unprecedented circumstances. The overall environment and its uncertainties increased the difficulty of planning events, performing in-person outreach, and connecting with both my liaison departments and broader units on campus.

I made use of my existing experience in lesson development and delivering training online to offer workshops online through the Zoom platform. This had the dual advantage of establishing a permanently online record of my lesson content, as well as expanding the accessibility of my instruction to anyone, instead of being limited to in-person attendance.

Although the campus re-opened to employees in Summer 2021, there was still a great deal of uncertainty through the Fall 2021 semester, with many classes being offered hybrid and many events remaining virtual. This resulted in delays for certain activities--for my IMLS-funded project, I led my project team to plan in-person meeting, not knowing what future COVID transmission levels or safety measures would be feasible or acceptable to attendees.

# AREAS OF SPECIALIZATION

* **Reproducibility**: promoting research practices that support "reproducibility" (the ability to generate identical or equivalent results to that of an existing publication using the same dataset and analysis procedures), encompassing data management, sharing intermediate products such as data and code, and accurate and rigorous reporting of statistical analyses.

* **Open research**: A philosophy of radical openness and transparency that may be applied to all facets of research. The open research ethos recognizes that many research problems are complex and thus benefit from teams of researchers working collectively and sharing information (e.g., open access and data sharing commitments for COVID-19 research)

* **Liaison librarianship**: supporting students, staff, and faculty in the health sciences through various activities such as: expert literature searching, teaching best practices in information searching and retrieval, developing relevant and appropriate library resources and collections, 

* **Diversity, equity, and inclusion**: cultivating environments and systems that are intentionally welcoming of individuals from all backgrounds, including historically and presently oppressed group identities, such as race, nationality, gender, sexuality, disability status, etc. 

# EFFORT REPORTED SINCE LAST PROMOTION (NOT TO EXCEED TEN YEARS), OR SINCE UF EMPLOYMENT, whichever is more recent 

```{r}
df <- readRDS("data/effort_perc.RDS")

# start table at `first_term`
first_term <- "Spring 2020"
last_row <- which(df[,1] == first_term)
if (length(last_row) == 1)
{
    df <- df[seq(from = 1, to = last_row), ]
}

format_effort_perc(df)
```

# EDUCATIONAL BACKGROUND

```{r, message = FALSE}
dat_degrees <- readRDS("data/degrees.RDS")
dat_degrees %>%
    mutate(Year = as.character(year(as.Date(Date)))) %>%
    select(-Date) %>%
    arrange(desc(Year)) %>%
    flextable() %>%
    set_table_properties(layout = "autofit") %>%
    theme_box() %>% 
    align(align = "center", part = "header")
```

# EMPLOYMENT

```{r, message = FALSE}
dat_jobs <- readRDS("data/jobs.RDS")
dat_jobs %>%
    format_jobs() %>%
    flextable() %>%
    set_table_properties(layout = "autofit") %>%
    theme_box() %>% 
    align(align = "center", part = "header")
```


# YEAR TENURE/PERMANENT STATUS WAS AWARDED BY UNIVERSITY OF FLORIDA

N/A

# TENURE AND PROMOTION CRITERIA

# TEACHING, ADVISING, AND INSTRUCTIONAL ACCOMPLISHMENTS

```{r, include = FALSE}
dat_teaching <- readRDS("data/teaching.RDS")
```

*NOTE: To support the teaching and research missions of the University, Library faculty are assigned to varying degrees to perform public, technical, archival, and administrative functions. These primary activities are referred to in the Libraries' T&P Criteria as "Professional Responsibilities" rather than "Teaching" to better reflect the unique and specialized activities in which Library faculty engage.*

```{r, include = FALSE}
carpentries_instructor_trainings <- filter(dat_teaching, 
                                           str_detect(title, "Carpentries Instructor Training"))

standalone_stats <- filter(dat_teaching, 
                           type == "standalone")
standalone_sessions <- NROW(standalone_stats)
standalone_attendees <- sum(as.numeric(standalone_stats$num_attendees))
```

As the reproducibility librarian, I strive to promote research practices that both improve reproducibility and make research more effective and efficient. One of the pillars of my work is to provide training and instruction in a variety of formats and settings.

In the for-credit course I co-teach with colleagues in HSCL and ARCS, "GMS 5909: Finding Biomedical Research Information and Communicating Science", I embed reproducibility as a core facet for the research process. Although this course primarily reaches graduate students in the Health Science Colleges, I expand my reach to other research disciplines and contexts through course-integrated instruction. For example, I regularly lead a session in "GMS 7877: Responsible Conduct of Biomedical Research", as well as in the Research Integrity Summer Seminar Series offered by the UF Office of Research. These sessions present reproducibility as a necessary component of rigorous and reliable research, in fitting with the overall application of these courses in satisfying training requirements in research integrity. In addition, I have taught guest lectures for courses in diverse departments across UF, such as Genomics, Biomedical Engineering, Latin American Studies, and Entomology & Nemotology, selecting specific reproducible research topics tailored for these different audiences. This coordination across the University of Florida reflects both the growing awareness of reproducibility as a cornerstone of research practices, and of my capability in providing effective instruction.

However, there are limitations to these forms of instruction in the topics that can be covered and the audiences that can be reached. Because research is so varied, reproducibility practices also span a large spectrum, and there is no "one size fits all" tool or method that works for everyone. Consequently, I have developed and teach an array of standalone workshops through the UF Libraries. To make these workshops relevant and engaging to researchers, I feature practical skills that can be implemented immediately, as well as follow-up resources for further training and practice. To maximize reach, I offer these workshops virtually through zoom, provide recordings to registered attendees (not just those that show up), and share the instructional materials as individual websites linked through https://guides.uflib.ufl.edu/reproducibility/lessons, to provide researchers with asynchronous access. Nevertheless, learners still find benefits to attending "live", as seen in my total count of `r standalone_attendees` attendees across `r standalone_sessions` sessions.

My ability to provide effective instruction in research practices is recognized, even beyond the University of Florida. My teaching has been sought out by external organizations, including the National Institutes of Health Office of Data Science Strategy and the African Society for Bioinformatics and Computational Biology. Both of these organizations host codeathon events where I have been an invited instructor for relevant tutorials, with positive feedback in the measured uptake of new practices during the events and invitations to return for future events.

In addition to teaching directly, I also look for alternative means to enhance my instructional impact. Thus, in summer 2021, I sought out and completed trainer training for The Carpentries, an international non-profit organization that develops and teaches practical and reproducible coding and data science skills to researchers. As a certified instructor trainer, I can train new instructors, sustaining both The Carpentries global organization, as well as the local chapter at UF (the UF Carpentries Club). To date, I have taught `r NROW(carpentries_instructor_trainings)` instructor training sessions to a total of `r sum(as.numeric(carpentries_instructor_trainings$num_attendees))` new instructors. 

```{r}
num_videos <- readRDS("data/videos.RDS") %>% NROW()
```

In collaboration with the UF Norman Fixel Institute for Neurological Diseases, I co-organize the Rigor and Reproducibility Seminar Series, which is funded by a T32 training grant to PIs Dawn Bowers and David Vaillancourt. To date, this seminar series has hosted `r num_videos` guest speakers to present on topics in research integrity, reproducibility, and open science - https://uf-repro.github.io/movementdisorders-seminar/ . The seminar series has been well-received, both with audiences at UF, and with representatives from the NIH, who have communicated interest in implementing the idea more broadly to support research integrity efforts.

# TEACHING EVALUATIONS

## UF Teaching Evaluations

**Summary Table**

<br />

```{r}
df <- readRDS("data/teaching_summary.RDS") %>%
    remove_empty_rows()
format_teaching_summary(df)
```

<br />

```{r}
df <- readRDS("data/teaching_evals.RDS")
format_teaching_eval(df)
```

**Additional Classes**

The majority of my instruction occurs in single session or multi-session workshops that receive no evaluations. These activities are divided into the following categories:

### Course-Integrated Instruction

```{r}
dat_teaching %>%
    filter(type == "course-integrated") %>%
    dplyr::mutate(other_instructor = ifelse(is.na(other_instructor), "", 
                                            glue::glue("co-instructor with {other_instructor}, ")),
                  print_header = glue::glue('**{course_id}: {title}** - *{session}*, {date}, {other_instructor}'),
                  print_instructor = glue::glue("  \nCourse Instructor: {instructor}"),
                  to_print = glue::glue("{print_header}  \n{print_instructor}\n", .trim = FALSE)) %>%
    dplyr::select(date, to_print) %>%
    print_data()
```

### Standalone Library Workshops

```{r}
dat_teaching %>%
    filter(type == "standalone") %>%
    group_by(title) %>%
    summarize(n = n(), 
              date = min(date)) %>%
    mutate(session_line = glue::glue("{n} {ifelse(n > 1, 'sessions', 'session')}"), 
           to_print = glue::glue('*{title}*, {session_line} since {year(date)}')) %>%
    print_data()
```

### Other Instruction

```{r}
dat_teaching %>%
    filter(type == "other", 
           is.na(outreach) | outreach == "n") %>%
    mutate(title = ifelse(is.na(session), title, glue::glue("{title}: {session}")), 
           to_print = glue::glue('*{title}*, {event_info}, {date}')) %>%
    print_data()
```

## Peer assessments

None

# EDUCATIONAL PORTFOLIO (if applicable)

N/A

# GRADUATE COMMITTEE ACTIVITIES

```{r}
df <- readRDS("data/grad_committees.RDS") %>%
    remove_empty_rows()

format_grad_committee(df)
```

# CONTRIBUTION TO DISCIPLINE/RESEARCH NARRATIVE

```{r}
dat_research <- readRDS("data/research.RDS")
oer_works <- filter(dat_research, type %in% c("OER")) %>%
    join_zenodo_stats()
```

There is growing interest and awareness of issues around replicability/reproducibility, and concomitant policies from institutions and funders. My work empowers researchers with the tools and training to navigate this changing landscape, investigates the effectiveness of different mechanisms for shifting practices, and addresses the structures that perpetuate barriers to equity and inclusion in the research ecosystem.

<!-- Reproducibility and replicability refer to the trustworthiness and robustness of research results. Following the definitions adopted by the National Academies of Sciences, Engineering, and Medicine, a study is **reproducible** if an independent researcher can perform an identical analysis on the same dataset, and achieve equivalent results; a **replication study** involves collecting new data and following the same procedures to test if the results of the initial study generalize. -->

*Reproducibility Training*

Because there are a multitude of factors that may cause irreproducibility, there is no consensus on the best approach to promote reproducibility. Thus, it is important for me to engage with the broader community of researchers and instructors. One of the ways I do this is through sharing my instructional materials as open educational resources. Doing so shows how my teaching has impacts beyond students, with my materials on the Zenodo repository amassing `r sum(oer_works$views)` views and 
`r sum(oer_works$downloads)` downloads.

I directly collaborate with others to share and discuss different approaches to reproducibility training. Following the "Research Reproducibility 2020: Educating for Reproducibility" virtual conference that I co-organized, I and the other members of the organizational team wrote a synthesis of the themes, published in the _Journal of Statistics and Data Science Education_. I also co-authored a case study of different approaches to reproducibility training, accepted for publication in the _Journal of the Medical Library Association_

As a recognized expert, I was invited to attend a workshop hosted by the NIH National Institute of Neurological Disorders and Stroke in May 2022 on "Catalyzing Communities of Research Rigor Champions". This event brought together leading researchers and institutional representatives to discuss how shifting the way research is done requires not just incentives, mandates, and education, but socio-cultural factors, such as local communities of practice.

*Open Science^[Although "open science" is the most common term, many aspects apply to research fields that are not considered part of science. I use "open science" here to refer broadly to "open research" or "open scholarship".] Practices*

One of the common pathways to improve reproducibility is to increase openness and transparency in research. This includes actions that are already established, such as sharing publications open access, as well as emergent, such as sharing data, analysis code, and pre-registered study protocols. Some of my work explores these boundaries, in order to provide better guidance to researchers, as well as shape research practice more broadly.

To explore the challenges and solutions in bringing openness and transparency to grant proposals, I am the PI on the project "Planning for Open Grants: Fostering a Transparent and Accessible National Research Proposal Infrastructure", funded by the Institute for Museum and Library Services. This project engages with stakeholders across research sectors, including researchers, administrators, funders, and technologists, and will complete in 2023. Outputs from the project include conference talks (1 completed, and 1 proposed) and publications (1 accepted for full submission to the _College & Research Libraries_ topical issue on "Open and Equitable Scholarly Communications"). 

With growing interest in open science, high-level organizations have created or plan to create implementation guidelines. In response to the 2022 call from UNESCO for feedback on the "UNESCO Recommendation on Open Science", I co-authored a commentary to provide input on several key areas, "Open Life Science (OLS) response to UNESCO global call for best practices in open science". This collaboration brought together our lived experience and expertise in open science education and open science communities to (hopefully) inform policy at the highest levels.

*Equity and Inclusion*

Open research is commonly considered to include aspects such as bringing research to the public, through open access and citizen science projects that invite the public to participate in research. This perspective can also be brought to bear on academic research systems and their practices in equity and inclusion. My work in this area includes advocating for more equality in job recognition of contributions to research. For example, I co-led a submitted paper on the need for better career support for research support specialists who play a vital role in supporting research, but who are not typically acknowledge as researchers, "A manifesto for rewarding and recognising Team Infrastructure Roles".

I also seek to cultivate environments that are more inclusive and welcoming. With my expertise in allyship skills and providing instruction in allyship skills, I co-authored a paper that provides an introduction to these skills and practices, "An Introduction to Ally Skills for Natural History Collections Professionals".

# CREATIVE WORKS OR ACTIVITIES

## Open Educational Resources

In keeping with my principles of opening up scholarly and teaching work, I share the contents of my standalone workshops as Open Educational Resources.

<br />

```{r, results = "asis"}
oer_works %>% 
    format_zenodo_stats() %>%
    format_research_other(my_bib, zenodo_text) %>% 
    mutate(to_print = glue::glue("{to_print} {zenodo_text}")) %>% 
    underline_first_author() %>%
    format_author() %>%
    print_data(prefix = "* ", sep = "\n\n", 
               empty_message = "None\n")
```

## Video recordings for "Rigor and Reproducibility Seminar Series"

This ongoing seminar series is jointly hosted by the UF Norman Fixel Institute for Neurological Diseases and the UF Health Science Center Libraries. Recordings are linked on https://uf-repro.github.io/movementdisorders-seminar/.

<br />

```{r}
dat_videos <- readRDS("data/videos.RDS")

dat_videos %>% 
    format_videos() %>%
    indicate_presenter() %>%
    format_author() %>%
    print_data(prefix = "* ", sep = "\n\n", 
               empty_message = "None\n")
```

## Libguides

* Research Reproducibility and Open Science - https://guides.uflib.ufl.edu/reproducibility  
2613 views between 2020-05-01 and 2022-11-04
* Health Outcomes and Biomedical Informatics - https://guides.uflib.ufl.edu/hobi  
286 views between 2020-05-01 and 2022-11-04
* CoM Graduate Program in Biomedical Sciences - https://guides.uflib.ufl.edu/BMS  
17 views between 2020-05-01 and 2022-11-04
* Biostatistics - https://guides.uflib.ufl.edu/biostats  
68 views between 2020-05-01 and 2022-11-04


<!-- MRT: If you have LibGuides they would go here and would include date of creation, date of update, and number of uses. For your creative works below, would be helpful to have dates and usage if that is possible. -->

## Other Creative Works

```{r, results = "asis"}
dat_research <- readRDS("data/research.RDS")
works <- filter(dat_research, type %in% c("other", "software", "preprint", "podcast")) %>%
    join_zenodo_stats()

works %>% 
    format_zenodo_stats() %>%
    format_research_other(my_bib, zenodo_text) %>%
    mutate(to_print = glue::glue("{to_print} {zenodo_text}")) %>% 
    underline_first_author() %>%
    format_author() %>%
    print_data(prefix = "* ", sep = "\n\n", 
               empty_message = "None\n")
```

# PATENTS AND COPYRIGHTS

None

# PUBLICATIONS

## Books, Sole Author
<!-- (Title, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Books, Co-authored
<!-- (Co-author(s), Title, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Books, Edited
<!-- (Editor, Co-editor(s), Title, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Books, Contributor of Chapter(s)
<!-- (Author, Co-author(s), Title of Book and Chapter, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Monographs
<!-- (Author, Co-author(s), Title, Series of Volume, if applicable, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Refereed Publications
<!-- (Author, Co-author(s), Title, Name of Journal or Publication, Volume, Date, Inclusive Pages) -->

```{r, results = "asis"}
dat_research <- readRDS("data/research.RDS")
pubs <- filter(dat_research, status %in% c("published", "forthcoming"))

pubs %>%
    format_research("paper", my_bib) %>%
    remove_IN() %>%
    underline_first_author() %>%
    format_author() %>%
    print_data(prefix = "", sep = "\n\n<br />\n\n", 
               empty_message = "None\n")
```

## Non-refereed Publications
<!-- Author, Co-author(s), Title, Name of Journal, Bulletin, Circular, or other Publication, Volume, Date, Inclusive Pages -->
None

## Bibliographies/Catalogs
<!-- Author, Co-author(s), Title, Publisher, Place of Publication, Date, Inclusive Pages -->
None

## Abstracts
<!-- Author, Co-author(s), Title, Name of Journal or Publication, Volume, Date, Inclusive Pages -->
None

## Reviews
<!-- Author, Co-author(s), Title and Author of Work Reviewed, Where Review was Published, Date, Inclusive Pages -->
None

## Miscellaneous
<!-- Author, Co-author(s), Title, Source of Publication, Date, Inclusive Pages -->




# LECTURES, SPEECHES, POSTERS PRESENTED AT PROFESSIONAL CONFERENCES/SEMINARS

```{r}
dat_talks <- readRDS("data/talks.RDS") %>%
    filter(type == "talk") %>%
    replace_na(list(invited = "n", location = ""))

outreach_instruction <- dat_teaching %>%
    filter(type == "other", outreach == "y")

```

## International

```{r}
combine_talks_and_outreach(dat_talks, outreach_instruction, locale = "international")
```

## National

```{r}
combine_talks_and_outreach(dat_talks, outreach_instruction, locale = "national")
```

## Regional

```{r}
combine_talks_and_outreach(dat_talks, outreach_instruction, locale = "regional")
```

## State

```{r}
combine_talks_and_outreach(dat_talks, outreach_instruction, locale = "state")
```

## Local

```{r}
combine_talks_and_outreach(dat_talks, outreach_instruction, locale = "local")
```

# SPONSORED PROJECTS

```{r, include = FALSE}
start_year <- year(report_start_date)
end_year <- year(report_end_date)
```

## Funded

### List of Funded Grants

```{r, include = FALSE}
dat_grants <- readRDS("data/grants.RDS")
```

#### List of Funding - Internal `r start_year` to `r end_year`

```{r, message = FALSE, results = "asis"}
grants <- filter(dat_grants, funder_loc == "internal")

if (NROW(grants) > 0)
{
    grants %>%
        format_grants_table() %>%
        print_grants_table()
} else {
    cat("None")
}
```

#### List of Funding - External `r start_year` to `r end_year`

```{r, message = FALSE, results = "asis"}
grants <-  filter(dat_grants, funder_loc == "external")

if (NROW(grants) > 0)
{
    grants %>%
        format_grants_table() %>%
        print_grants_table()
}
```

<br />

### Summary of Grant Funding

```{r}
dat <- data.frame(ROLE = c("Principal Investigator", "Co-Principal Investigator", "Investigator", "Senior Personnel", "Sponsor of Junior Faculty", "Totals"), 
                  TOTAL = c(99833, 0, 8697, 0, 0, 108530), 
                  `Direct Costs` = c(75289, 0, 6675, 0, 0, 81964), 
                  `Indirect Costs` = c(24544, 0, 2022, 0, 0, 26566))

dat %>%
    flextable() %>%
    set_table_properties(layout = "autofit") %>%
    theme_box() %>%
    align(align = "center", part = "header") %>%
    align(align = "center", i = 6, j = 1)

```

### Short Narrative of Grant Funding

**Planning for Open Grants: Fostering a Transparent and Accessible National Research Proposal Infrastructure** (ongoing)

The funds for this grant support work on a planning project to explore the social and technical issues around an open repository, including hiring two graduate student research fellows, stipends for an external advisory board, and conference travel. As the PI, I lead the project team, coordinate the activities, and supervise the student hires.

**Supplement: GatorSTAR: A New MARC** (ongoing)

The funds for this grant support salaries for team members and the creation and implementation of training modules to educate students on how to share data following the FAIR (Findable Accessible Interoperable Reusable) guidelines. As an investigator for this project, I co-create the materials and assist with the evaluation of the lesson effectiveness.

**Educating for Reproducibility: Pathways to Integrity**

The funds for this grant supported salaries and the hosting of a virtual conference on education in reproducibility across different research disciplines and career stages. As an investigator for this project, I was a co-planner for the conference, and facilitated the event itself by moderating and hosting sessions.

# SERVICE NARRATIVE 

<!-- As with my research and teaching, the overarching goal of my service work is to improve research practices in the service of reproducibility and openness. Because service work does not often directly affect these qualities, my activities generally involve cultivating resources, communities, and infrastructure to support the research activities of others. -->

With my recognized expertise in data science and open science, I have been invited to evaluate funding proposals for several international organizations. In 2020, I began serving on the Event Fund Selection Committee for _Code for Science & Society_, a nonprofit organization that works to "advance the power of data to improve the social and economic lives of all people through public education, scientific research, and technology development and deployment". I worked with the other committee members to evaluate and recommend for funding, events that build inclusive data science communities. Through 3 rounds of awards, we supported 37 events, representing 27 countries and 6 continents. Before stepping down in Spring 2022, I provided input on the application and review process. In 2021, I was an invited grant reviewer for the Wellcome Trust - Data for Science and Health Award, providing evaluation of a research proposal in the area of ecological modeling and data science.

Some of my most impactful work is in organizing communities to work together. As the chair of the Medical Library Association Data Caucus (group with over 200 members), I coordinate meetings of librarians who provide data services. As an outgrowth of this group, I created and now facilitate a working group that creates guidance materials for the new NIH Data Management and Sharing Policy. This new policy goes into effect in January 2023 and mandates Data Management and Sharing Plans to accompany all funding proposals, with the intent to maximize data sharing and re-use. Be leveraging collective effort, the working group reduces redundancy among those of us that support researchers in complying with the policy, and also helps to ensure more comprehensive guidance. This group has created several public resources (https://osf.io/uadxr/) that are being used and re-shared (for example, by the Network of the National Library of Medicine - https://www.nnlm.gov/guides/nnlm-toolkit-nih-data-management-and-sharing-policy ). To support honoraria for contributors and meeting facilitators, I asked for and received funding from professional organizations (RDAP - Research Data Access and Preservation Association, and the Network of the National Library of Medicine National Center for Data Services) .

In my role as chair of the UF Libraries Open Access Committee, I lead the group in supporting open access publishing at the university. These activities include: creating outreach messaging, promoting of read-and-publish initiatives, and hosting a discussion panel for Open Access Week in October 2022. To bring further transparency to the committee's decision making, we are preparing to release our evaluation rubric for open access initiatives. This will promote engagement with the broader community of open access advocates across institutions and research sectors.

I have served on 4 search committees for the UF Libraries (1 ongoing), including one as chair. In addition to ensuring the hiring of excellently qualified personnel, I have acted as the Diversity, Equity, and Inclusion (DEI) search advocate--these additional responsibilities include promoting the position to recruit individuals from diverse backgrounds, implementing the search to ensure a fair and equitable process, and making sure that candidates are evaluated on their ability to contribute to the DEI mission of the libraries and the university.

Many of my service activities revolve around promoting an equitable and inclusive environment. In my work with UF student-facing committees (e.g., UF Libraries Student Engagement Committee, UF Libraries Fall Fest Committee, HSCL Diversity, Equity, and Inclusion Team), I strive to design events to be broadly inclusive, especially for online students who are not able to participate in in-person events in Gainesville. I also build inclusion 
as a member of the Code of Conduct Committee for _Reproducibility for Everyone_, a global community that shares instructional modules and teaches workshops on reproducibility. In support of this work, I have received training in Code of Conduct enforcement, and co-developed, with the rest of the committee, detailed procedures for responding to code of conduct incidents, should they arise.

As an associate editor at _Methods for Ecology & Evolution_, I am responsible for handling approximately 6 manuscripts a year: identifying and recruiting peer reviewers, reading the manuscript and its reviews, and making a recommendation to the senior editors. This work is rewarding in giving me the opportunity to guide authors in improving their written communications, and to be encouraging to early career authors, including students. In September 2022, I was invited to join the editorial board at _Ecology_ as an editor of the "Data Paper" submission format. In this new position, I am refining the standards to enhance data re-use, while streamlining the process for submitting authors.

<!-- 
In addition to promoting reproducibility and open research practices through training, I strive to create environments where better practices are normalized and encouraged.  and providing suitable resources that lower the burden to change.


I continually seek out opportunities to enhance the impact of my service, including developing and deploying teaching or leadership skills. 
-->

# UNIVERSITY GOVERNANCE AND SERVICE

```{r, include = FALSE, message = FALSE}
dat_service <- readRDS("data/service.RDS")

uni_service <- filter(dat_service, setting %in% c("university", "library"))
dat_service <- anti_join(dat_service, uni_service)
```

## University

```{r}
print_service(uni_service, sublocale = "university")
```

## College

```{r}
print_service(uni_service, sublocale = "college")
```

## Department/Center

```{r}
print_service(uni_service, sublocale = "department")
```

# CONSULTATIONS OUTSIDE THE UNIVERSITY

None

# EDITOR OF SCHOLARLY JOURNALS, SERVICE OR EDITORIAL ADVISORY BOARDS, REVIEWER FOR SCHOLARLY JOURNALS

## Editor

```{r, message = FALSE}
dat_editor <- filter(dat_service, stringr::str_detect(dat_service$role, "editor"))
dat_service <- anti_join(dat_service, dat_editor)

dat_editor %>%
    format_service() %>%
    print_data(prefix = "* ", sep = "\n\n")
```

## Editorial Advisory Boards

None

## Reviewer for Scholarly Journal

```{r}
dat_reviews <- readRDS("data/reviews.RDS")

dat_reviews %>%
    format_reviews() %>%
    print_data(prefix = "* ", sep = "\n\n", 
               empty_message = "None\n")
    
```

## Book Manuscripts Reviewed

None

# INTERNATIONAL ACTIVITIES

<!-- I’d use this space as an opportunity to reiterate all of those international invitations that you’ve received. I do think I would list them in the section on presentations (rather than instruction), and just allude back to them here a little more obviously than you have done. -->

Reproducibility is a multi-faceted issue that presents a multitude of challenges and possible solutions. In engaging with international collaborators, stakeholders, and audiences, I am able to both share with and learn from a diverse set of backgrounds and experiences that enhance the impact of my work. This is particularly relevant when interacting with reproducibility and open science groups outside the US and thinking about what kinds of multi-institutional or multi-sector partnerships can shift research practices in the US, Florida, the University, and more local settings. Conversely, my service to international communities and professional organizations enables me to stay on the forefront of advances and practices in the areas of research reproducibility and open research.

# EXTENSION PROGRAMS (for IFAS only)

N/A

# CLINICAL SERVICE, CLINICAL ACTIVITIES, OR CLINICAL PORTFOLIO

N/A

# SERVICE TO SCHOOLS

None

# MEMBERSHIP AND ACTIVITIES IN THE PROFESSION

## MEMBERSHIPS

```{r, include = FALSE, message = FALSE}
memberships <- filter(dat_service, activity == "n")
```

### International

```{r}
print_memberships(memberships, locale = "international")
```

### National

```{r}
print_memberships(memberships, locale = "national")
```

### Regional

```{r}
print_memberships(memberships, locale = "regional")
```

### State

```{r}
print_memberships(memberships, locale = "state")
```

### Local

```{r}
print_memberships(memberships, locale = "local")
```

## ACTIVITIES IN THE PROFESSION

```{r, include = FALSE, message = FALSE}
activities <- filter(dat_service, activity == "y")
```

### International

```{r}
activities %>%
    filter(locale == "international") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### National

```{r}
activities %>%
    filter(locale == "national") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### Regional

```{r}
activities %>%
    filter(locale == "regional") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### State

```{r}
activities %>%
    filter(locale == "state") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### Local

```{r}
activities %>%
    filter(locale == "local") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

# HONORS

```{r, include = FALSE}
awards <- readRDS("data/awards.RDS")
```

## International

```{r}
print_awards(awards, locale = "international")
```

## National

```{r}
print_awards(awards, locale = "national")
```

## Regional

```{r}
print_awards(awards, locale = "regional")
```

## State

```{r}
print_awards(awards, locale = "state")
```

## Local

```{r}
print_awards(awards, locale = "local")
```

# CHAIR’S LETTER

# DEAN’S LETTER

# SAMPLE LETTER TO EVALUATORS

# BIO-SKETCHES OF INDIVIDUALS WRITING SOLICITED LETTERS OF EVALUATION and LETTERS OF EVALUATION

<!-- MRT: Although you won’t be asking for letters, this is a great time to think about who you might ask. You could list them here with a short explanation as to why. -->


# COPIES OF THE LAST FIVE ANNUAL LETTERS OF EVALUATION

# FURTHER INFORMATION

## Submitted Talks

```{r}
print_talks(dat_talks, locale = NULL, submitted = TRUE, refereed_label = "In Review")
```

## Submitted Manuscripts

```{r}
dat_research <- readRDS("data/research.RDS")
pubs <- filter(dat_research, 
               str_detect(status, "accepted|in review|submitted|forthcoming"))

pubs %>%
    format_research("paper", my_bib) %>%
    remove_IN() %>%
    underline_first_author() %>%
    format_author() %>%
    print_data(prefix = "", sep = "\n\n<br />\n\n", 
               empty_message = "None\n")
```

