---
output: 
  word_document:
    reference_docx: "packet_styles.docx"
---

```{r setup, include = FALSE}
library(tidyverse)
library(lubridate)
library(googlesheets4)
library(RefManageR)
library(activityReporteR)
library(flextable)

report_start_date <- as.Date("2020-05-01")
report_end_date <- as.Date("2100-01-01")

data_gs_url <- "https://docs.google.com/spreadsheets/d/11XRsF-MupYcnZlykUe6YHAGe1A16CxJyq9nT3oSbDeg/edit#gid=0"
gs4_auth("haoye@ufl.edu")

data_bib_file <- "my_lib.bib"
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           cite.style = "apa",
           style = "markdown",
           max.names = Inf, 
           hyperlink = FALSE,
           dashed = FALSE, 
           use.misc.default.format = TRUE)
my_bib <- ReadBib(data_bib_file, check = FALSE)

dept_name <- "Academic Research Consulting & Services"

set_flextable_defaults(
    font.family = "Times New Roman", 
    font.size = 11, 
    border.color = "black", 
    table.layout = "fixed", 
    padding.top = 3, padding.bottom = 1
)

source("R/download_gs_data.R")
source("R/format_data.R")
source("R/format_word_tables.R")
source("R/print_data.R")

knitr::opts_chunk$set(echo = FALSE, results = "asis")
```

```{r check data sources}
data_files <- c("data/degrees.RDS", 
                "data/jobs.RDS", 
                "data/effort_perc.RDS", 
                "data/teaching_summary.RDS", 
                "data/teaching_evals.RDS", 
                "data/grad_committees.RDS",
                "data/teaching.RDS", 
                "data/research.RDS",
                "data/videos.RDS", 
                "data/grants.RDS", 
                "data/service.RDS", 
                "data/reviews.RDS", 
                "data/awards.RDS", 
                "data/talks.RDS")
data_files_found <- file.exists(here::here(data_files))
if (!all(data_files_found))
{
    missing_files <- paste0("file '", 
                            data_files[!data_files_found], 
                            "' not found")
    vapply(missing_files, warning, "", call. = FALSE)
}
```

**In all of your packet, try to avoid phrases like “helped with” or “assisted with” if it can be described in a stronger way. For example, instead of saying helped with planner, say you were a co-planner. Everything should sound like you are a faculty member doing professional level work.**

# NOMINEE INFORMATION COVER SHEET 

<!--

The cover sheet automatically gets added after the PDF is uploaded into UF's OPT system.
-->

# BRIEF DESCRIPTION OF JOB DUTIES 

<!-- Briefly describe your assigned duties and responsibilities. Provide context for these responsibilities (ie. the relevance and importance to your discipline and UF -->
<!-- Describe the duties of your position – this is not really the place for first person input (instead of ‘I do this and I do that’, it should be a description of the duties). Take advantage of this opportunity to ‘translate’ your work for reviewers who are unfamiliar with librarianship. -->

<!-- MRT: I split the first sentence into 2 because it was pretty long, and most people won’t be familiar with what you do so important to make it easy for them. I’d be real obvious about how ARCS serves the whole campus, and that ARCS is Smathers Libraries -->

As the reproducibility librarian, I am responsible for developing and executing on an institutional strategy for education and support of trans-disciplinary research reproducibility and open science for the University of Florida community. These responsibilities include programming for and support of information retrieval/storage, data- and computational workflows, responsible conduct of research, and open scholarship broadly defined (e.g. open access, publishing data and code, preprints). I also serve as the liaison librarian to several departments and programs in the College of Medicine and College of Public Health and Health Professions: Biostatistics, Health Outcomes and Biomedical Informatics, and the Graduate Program in Biomedical Sciences. My position provides interdisciplinary information consultation services in a variety of modes, designs workshops to promote research reproducibility, performs course-integrated instruction, and participates in the Smathers Libraries' teaching initiatives. In addition, I support special projects and programs related to the overall mission of the Academic Research Consulting & Services department, including coordinating and promoting programs and services, such as the Student HiPerGator Sponsorship program. I serve on and lead committees within UF, and for national and international professional organizations, when such responsibilities complement or directly relate to promoting research reproducibility. My scholarship explores new modes and models for open research broadly and possible interventions to shift existing practices, such as through instruction, technical infrastructure, and sociocultural incentives. 


## Impact of COVID pandemic on Job Duties
<!-- In this optional section faculty may provide a statement regarding the impact of the COVID-19 pandemic on the nominee’s professional life -- up to 500 words. This statement should explain how the nominee adjusted/compensated for pandemic-related difficulties impacting their research, teaching, clinics, extension or service. Please see http://aa.ufl.edu/policies/tenure-and-promotion-information/ for more details. This was a new section beginning in 2021. -->

<!-- MRT: I’d probably add something here about how long the libraries were closed to in-person. -->


The COVID pandemic had a substantial and indeterminate effect on my professional responsibilities. In between my hire and my start in May 2020, the university closed, without a specific plan for re-opening. On top of the challenges of starting a new position, there were many obstacles resulting from operating in unprecedented circumstances. The overall environment and its uncertainties increased the difficulty of planning events, performing in-person outreach, and connecting with both my liaison departments and broader units on campus.

I made use of my existing experience in lesson development and delivering training online to offer workshops online through the Zoom platform. This had the dual advantage of establishing a permanently online record of my lesson content, as well as expanding the accessibility of my instruction to anyone, instead of restricting it to whoever is able to attend in-person.


# AREAS OF SPECIALIZATION

* **Reproducibility**: promoting research practices that support "reproducibility" (the ability to generate identical or equivalent results to that of an existing publication using the same dataset and analysis procedures), encompassing data management, sharing intermediate products such as data and code, and honest reporting of statistical analyses.

* **Open research**: A philosophy of radical openness and transparency to as many facets of research as possible, recognizing that many research problems are complex and benefit from teams of researchers working collectively and sharing information (e.g. open science commitments for COVID-19 research)

* **Liaison librarianship**: supporting students, staff, and faculty in the health sciences through various activities including: expert literature searching, teaching best practices in information searching and retrieval, developing relevant and appropriate library resources and collections, 

* **Diversity, equity, and inclusion**: cultivating environments and systems that are intentionally welcoming of individuals from all backgrounds, including historically and presently oppressed group identities, such as race, nationality, gender, sexuality, disability status, etc. 

# EFFORT REPORTED SINCE LAST PROMOTION (NOT TO EXCEED TEN YEARS), OR SINCE UF EMPLOYMENT, whichever is more recent 

```{r}
df <- readRDS("data/effort_perc.RDS")

# start table at `first_term`
first_term <- "Spring 2020"
last_row <- which(df[,1] == first_term)
if (length(last_row) == 1)
{
    df <- df[seq(from = 1, to = last_row), ]
}

format_effort_perc(df)
```

# EDUCATIONAL BACKGROUND

```{r, message = FALSE}
dat_degrees <- readRDS("data/degrees.RDS")
dat_degrees %>%
    mutate(Year = as.character(year(as.Date(Date)))) %>%
    select(-Date) %>%
    arrange(desc(Year)) %>%
    flextable() %>%
    set_table_properties(layout = "autofit") %>%
    theme_box() %>% 
    align(align = "center", part = "header")
```

# EMPLOYMENT

```{r, message = FALSE}
dat_jobs <- readRDS("data/jobs.RDS")
dat_jobs %>%
    format_jobs() %>%
    flextable() %>%
    set_table_properties(layout = "autofit") %>%
    theme_box() %>% 
    align(align = "center", part = "header")
```


# YEAR TENURE/PERMANENT STATUS WAS AWARDED BY UNIVERSITY OF FLORIDA

N/A

# TENURE AND PROMOTION CRITERIA

# TEACHING, ADVISING, AND INSTRUCTIONAL ACCOMPLISHMENTS

```{r, include = FALSE}
dat_teaching <- readRDS("data/teaching.RDS")
```

*NOTE: To support the teaching and research missions of the University, Library faculty are assigned to varying degrees to perform public, technical, archival, and administrative functions. These primary activities are referred to in the Libraries' T&P Criteria as "Professional Responsibilities" rather than "Teaching" to better reflect the unique and specialized activities in which Library faculty engage.*



```{r, include = FALSE}
carpentries_instructor_trainings <- filter(dat_teaching, 
                                           str_detect(title, "Carpentries Instructor Training"))
```

For example, in summer 2021, I completed trainer training for The Carpentries (The Carpentries is an international non-profit organization that develops and teaches coding and data science skills to researchers), certifying me as an instructor trainer for the organization. My activities for this organization and the local chapter at UF (the UF Carpentries Club) then shifted from serving as an instructor for coding workshops to training and certifying new instructors, to grow the community and sustain excellence in promoting effective computational and data skills. To date, I have taught `r NROW(carpentries_instructor_trainings)` instructor trainings with a total of `r sum(as.numeric(carpentries_instructor_trainings$num_attendees))` new instructors.


* **Course-Integrated Instruction** - guest lectures offered as part of for-credit courses at UF (spanning general reproducibility topics and across different colleges and departments)
* **Standalone Library Workshops** - virtual sessions hosted by the Libraries, and open to all UF students, staff, and faculty
* **Other Instruction, UF** - other instruction hosted at the UF, usually in the form of workshops with targeted or broad audiences
* **Other Instruction, Outreach** - other instruction, performed as outreach on behalf of other organizations, and in my areas of expertise


I continually seek out opportunities to enhance the impact of my service, including developing and deploying teaching or leadership skills.

My expertise in reproducibility training has been sought out 


# TEACHING EVALUATIONS

## UF Teaching Evaluations

**Summary Table**

<br />

```{r}
df <- readRDS("data/teaching_summary.RDS") %>%
    remove_empty_rows()
format_teaching_summary(df)
```

<br />

```{r}
df <- readRDS("data/teaching_evals.RDS")
format_teaching_eval(df)
```

**Additional Classes**

The majority of my instruction occurs in single session or multi-session workshops that receive no evaluations. These activities are divided into the following categories:

### Course-Integrated Instruction

```{r}
dat_teaching %>%
    filter(type == "course-integrated") %>%
    dplyr::mutate(other_instructor = ifelse(is.na(other_instructor), "", 
                                            glue::glue("co-instructor with {other_instructor}, ")),
                  print_header = glue::glue('**{course_id}: {title}** - *{session}*, {date}, {other_instructor}'),
                  print_instructor = glue::glue("  \nCourse Instructor: {instructor}"),
                  to_print = glue::glue("{print_header}  \n{print_instructor}\n", .trim = FALSE)) %>%
    dplyr::select(date, to_print) %>%
    print_data()
```

### Standalone Library Workshops

```{r}
dat_teaching %>%
    filter(type == "standalone") %>%
    group_by(title) %>%
    summarize(n = n(), 
              date = min(date)) %>%
    mutate(session_line = glue::glue("{n} {ifelse(n > 1, 'sessions', 'session')}"), 
           to_print = glue::glue('*{title}*, {session_line} since {year(date)}')) %>%
    print_data()
```

### Other Instruction, UF

```{r}
dat_teaching %>%
    filter(type == "other", 
           is.na(outreach) | outreach == "n") %>%
    mutate(title = ifelse(is.na(session), title, glue::glue("{title}: {session}")), 
           to_print = glue::glue('*{title}*, {event_info}, {date}')) %>%
    print_data()
```

### Other Instruction, Outreach

```{r}
dat_teaching %>%
    filter(type == "other", outreach == "y") %>%
    mutate(title = ifelse(is.na(session), title, glue::glue("{title}: {session}")), 
           to_print = glue::glue('*{title}*, {event_info}, {date}')) %>%
    print_data()
```



## Peer assessments

None

# EDUCATIONAL PORTFOLIO (if applicable)

N/A

# GRADUATE COMMITTEE ACTIVITIES

```{r}
df <- readRDS("data/grad_committees.RDS") %>%
    remove_empty_rows()

format_grad_committee(df)
```

# CONTRIBUTION TO DISCIPLINE/RESEARCH NARRATIVE

Research is undergoing a massive increase in interest and awareness of issues around replicability/reproducibility, and concomitant policies and expectations from institutions and funders. My research aims primarily to empower researchers with the tools and training necessary to meet a changing research landscape, while also addressing systemic problems in equity and inclusion in the academic research ecosystem.

Briefly, reproducibility and replicability refer to the trustworthiness and robustness of research results. Following the definitions adopted by the National Academies of Sciences, Engineering, and Medicine, a study is **reproducible** if an independent researcher can perform an identical analysis on the same dataset, and achieve equivalent results; in contrast, a **replication study** involves collecting new data and following the same procedures to test if the results of the initial study generalize.

*Reproducibility Training*

Because there are a multitude of factors that may cause irreproducibility, there is no consensus on the best approach to ensure reproducibility. One of the pillars of my work is in developing training in reproducible research practices. 
This includes workshops that I have shared as open educational resources, in addition to trainings developed in conjunction with others.

Work to identify different approaches in training (RR 2020 paper, JMLA paper)

Reproducibility and open research practices are challenging to shift for a number of reasons, including
too many things to learn
no "one size fits all" tool or method for everyone
limited reward or recognition, with the potential for a great deal of time, effort, and other investment.


*Reproducibility Practices*

documents reproducibility, organize our understanding of different facets, and promote approaches that enable researchers to identify pathways for improving reproducibility that work best for their current set of practices and for their research approach and discipline. For example, using git/github or a version control system is often touted as an important tool for reproduciblity; however it is challenging to learn, with few immediate benefits, and not well-suited for non-computational research workflows.



*Equity and Inclusion*

open research can shift power
I seek to create more equity and inclusion in academic research spaces. allyship skills and advocacy for systemic changes to better recognize and reward individuals in research support roles (e.g. research computing, libraries, research software engineering)



# CREATIVE WORKS OR ACTIVITIES

## Open Educational Resources

In keeping with my principles of opening up scholarly and teaching work, I share the contents of my standalone workshops as Open Educational Resources.

<br />

```{r, results = "asis"}
dat_research <- readRDS("data/research.RDS")
works <- filter(dat_research, type %in% c("OER"))

works %>% 
    format_research_other(my_bib) %>%
    append_zenodo_stats() %>%
    underline_first_author() %>%
    format_author() %>%
    print_data(prefix = "* ", sep = "\n\n", 
               empty_message = "None\n")
```

## Video recordings for "Rigor and Reproducibility Seminar Series"

This ongoing seminar series is jointly hosted by the UF Normal Fixel Institute for Neurological Diseases and the UF Health Science Center Libraries. Recordings are linked on https://uf-repro.github.io/movementdisorders-seminar/.

<br />

```{r}
dat_videos <- readRDS("data/videos.RDS")

dat_videos %>% 
    format_videos() %>%
    indicate_presenter() %>%
    format_author() %>%
    print_data(prefix = "* ", sep = "\n\n", 
               empty_message = "None\n")
```

## Libguides

* Research Reproducibility and Open Science - https://guides.uflib.ufl.edu/reproducibility  
2613 views between 2020-05-01 and 2022-11-04
* Health Outcomes and Biomedical Informatics - https://guides.uflib.ufl.edu/hobi  
286 views between 2020-05-01 and 2022-11-04
* CoM Graduate Program in Biomedical Sciences - https://guides.uflib.ufl.edu/BMS  
17 views between 2020-05-01 and 2022-11-04
* Biostatistics - https://guides.uflib.ufl.edu/biostats  
68 views between 2020-05-01 and 2022-11-04


<!-- MRT: If you have LibGuides they would go here and would include date of creation, date of update, and number of uses. For your creative works below, would be helpful to have dates and usage if that is possible. -->

## Other Creative Works

```{r, results = "asis"}
dat_research <- readRDS("data/research.RDS")
works <- filter(dat_research, type %in% c("other", "software", "preprint", "podcast"))

works %>% 
    format_research_other(my_bib) %>%
    append_zenodo_stats() %>%
    underline_first_author() %>%
    format_author() %>%
    print_data(prefix = "* ", sep = "\n\n", 
               empty_message = "None\n")
```



# PATENTS AND COPYRIGHTS

None

# PUBLICATIONS

## Books, Sole Author
<!-- (Title, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Books, Co-authored
<!-- (Co-author(s), Title, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Books, Edited
<!-- (Editor, Co-editor(s), Title, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Books, Contributor of Chapter(s)
<!-- (Author, Co-author(s), Title of Book and Chapter, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Monographs
<!-- (Author, Co-author(s), Title, Series of Volume, if applicable, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Refereed Publications
<!-- (Author, Co-author(s), Title, Name of Journal or Publication, Volume, Date, Inclusive Pages) -->

```{r, results = "asis"}
dat_research <- readRDS("data/research.RDS")
pubs <- filter(dat_research, status %in% c("published", "forthcoming"))

pubs %>%
    format_research("paper", my_bib) %>%
    remove_IN() %>%
    underline_first_author() %>%
    format_author() %>%
    print_data(prefix = "", sep = "\n\n<br />\n\n", 
               empty_message = "None\n")
```

## Non-refereed Publications
<!-- Author, Co-author(s), Title, Name of Journal, Bulletin, Circular, or other Publication, Volume, Date, Inclusive Pages -->
None

## Bibliographies/Catalogs
<!-- Author, Co-author(s), Title, Publisher, Place of Publication, Date, Inclusive Pages -->
None

## Abstracts
<!-- Author, Co-author(s), Title, Name of Journal or Publication, Volume, Date, Inclusive Pages -->
None

## Reviews
<!-- Author, Co-author(s), Title and Author of Work Reviewed, Where Review was Published, Date, Inclusive Pages -->
None

## Miscellaneous
<!-- Author, Co-author(s), Title, Source of Publication, Date, Inclusive Pages -->




# LECTURES, SPEECHES, POSTERS PRESENTED AT PROFESSIONAL CONFERENCES/SEMINARS

```{r}
dat_talks <- readRDS("data/talks.RDS") %>%
    filter(type == "talk")
```

## International

```{r}
print_talks(dat_talks, locale = "international")
```

## National

```{r}
print_talks(dat_talks, locale = "national")
```

## Regional

```{r}
print_talks(dat_talks, locale = "regional")
```

## State

```{r}
print_talks(dat_talks, locale = "state")
```

## Local

```{r}
print_talks(dat_talks, locale = "local")
```

# SPONSORED PROJECTS

```{r, include = FALSE}
start_year <- year(report_start_date)
end_year <- year(report_end_date)
```

## Funded

### List of Funded Grants

```{r, include = FALSE}
dat_grants <- readRDS("data/grants.RDS")
```

#### List of Funding - Internal `r start_year` to `r end_year`

```{r, message = FALSE, results = "asis"}
grants <- filter(dat_grants, funder_loc == "internal")

if (NROW(grants) > 0)
{
    grants %>%
        format_grants_table() %>%
        print_grants_table()
} else {
    cat("None")
}
```

#### List of Funding - External `r start_year` to `r end_year`

```{r, message = FALSE, results = "asis"}
grants <-  filter(dat_grants, funder_loc == "external")

if (NROW(grants) > 0)
{
    grants %>%
        format_grants_table() %>%
        print_grants_table()
}
```

### Summary of Grant Funding

```{r}
dat <- data.frame(ROLE = c("Principal Investigator", "Co-Principal Investigator", "Investigator", "Senior Personnel", "Sponsor of Junior Faculty", "Totals"), 
                  TOTAL = c(99833, 0, 8697, 0, 0, 108530), 
                  `Direct Costs` = c(75289, 0, 6675, 0, 0, 81964), 
                  `Indirect Costs` = c(24544, 0, 2022, 0, 0, 26566))

dat %>%
    flextable() %>%
    set_table_properties(layout = "autofit") %>%
    theme_box() %>%
    align(align = "center", part = "header") %>%
    align(align = "center", i = 6, j = 1)

```

### Short Narrative of Grant Funding

**Planning for Open Grants: Fostering a Transparent and Accessible National Research Proposal Infrastructure** (ongoing)

The funds for this grant support work on a planning project to explore the social and technical issues around an open repository, including hiring two graduate student research fellows, stipends for an external advisory board, and conference travel. As the PI, I lead the project team, coordinate the activities, and supervise the student hires.

**Supplement: GatorSTAR: A New MARC** (ongoing)

The funds for this grant support salaries for team members and the creation and implementation of training modules to educate students on how to share data following the FAIR (Findable Accessible Interoperable Reusable) guidelines. As an investigator for this project, I co-create the materials and assist with the evaluation of the lesson effectiveness.

**Educating for Reproducibility: Pathways to Integrity**

The funds for this grant supported salaries and the hosting of a virtual conference on education in reproducibility across different research disciplines and career stages. As an investigator for this project, I was a co-planner for the conference, and facilitated the event itself by moderating and hosting sessions.

# SERVICE NARRATIVE 

<!-- As with my research and teaching, the overarching goal of my service work is to improve research practices in the service of reproducibility and openness. Because service work does not often directly affect these qualities, my activities generally take on the form of cultivating resources, communities, and infrastructure to indirectly support the research activities of others. -->

With my recognized expertise in data science and open science practices, I have been called upon to evaluate funding proposals for several international organizations. As a member of the Event Fund Selection Committee for Code for Science & Society, I and the other committee members evaluated and recommended for funding, a variety of events that build inclusive data science communities. Through 3 rounds of awards, we supported 37 events, representing 27 countries and 6 continents. To sustain continued operations, I provided input on the application and review process, before stepping down in Spring 2022. In 2021, I was an invited grant reviewer for the Wellcome Trust - Data for Science and Health Award, providing evaluation of a research proposal in the area of ecological modeling and data science.

To increase my impact, I organize and cultivate communities to share information and leverage group effort. As the chair of the Medical Library Association Data Caucus (group with over 200 members), I coordinate meetings of librarians who provide data services. As an outgrowth of this group, I created and now facilitate a working group that creates guidance materials for the NIH Data Management and Sharing Policy that goes into effect in January 2023. By working together, this group reduces redundance in effort, and ensures more comprehensive coverage of the policy, So far, this group has created several public resources (https://osf.io/uadxr/). In addition to coordinating this group, I also reached out to professional organizations (RDAP - Research Data Access and Preservation Association, and the Network of the National Library of Medicine National Center for Data Services) to support honoraria for contributors and meeting facilitators. 

In my role as chair of the UF Libraries Open Access Committee, I lead the group in supporting open access publishing at the university. These activities include: creating outreach messaging, promoting of read-and-publish initiatives, and hosting a discussion panel for Open Access Week in October 2022. To bring further transparency to the committee's decision making process, we are preparing to release our evaluation rubric for open access initiatives. This will enable further engagement with the larger community of open access advocates across institutions and research sectors.

I have served on 4 search committees for the UF Libraries (1 ongoing), including one as chair. In addition to ensuring the hiring of excellently qualified personnel, I have acted as the Diversity, Equity, and Inclusion (DEI) search advocate--these additional responsibilities include promoting the position broadly to recruit individuals from diverse backgrounds, suggesting and enacting changes to ensure a fair and equitable process, and making sure that candidates are evaluated on their ability to contribute to the DEI mission of the libraries and the university.

Many of my service activities revolve around promoting an equitable and inclusive environment. In my work with UF student-facing committees (e.g. UF Libraries Student Engagement Committee, UF Libraries Fall Fest Committee, HSCL Diversity, Equity, and Inclusion Team), I strive to design events to be broadly inclusive, especially for online students who are not able to participate in in-person events in Gainesville. As a member of the Reproducibility for Everyone Code of Conduct Committee, I extend this approach to a globally-distributed community. In support of this work, I have received training in Code of Conduct enforcement, and co-developed, with the rest of the committee, detailed procedures for responding to code of conduct incidents, should they arise.

As an associate editor at _Methods for Ecology & Evolution_, I am responsible for handling approximately 6 manuscripts a year: identifying and recruiting peer reviewers, reading the manuscript and its reviews, and making a recommendation to the senior editors. Although I have found this to be more work than performing a peer review, it is also more rewarding. I am able to guide authors in improving their written communications, and to be encouraging to early career authors, including students. In September 2022, I was invited to join the editorial board at _Ecology_ as an editor of the "Data Paper" submission format. In this new position, I am refining the standards to enhance data re-use, while streamlining the process for submitting authors.

<!-- 
In addition to promoting reproducibility and open research practices through training, I strive to create environments where better practices are normalized and encouraged.  and providing suitable resources that lower the burden to change.


I continually seek out opportunities to enhance the impact of my service, including developing and deploying teaching or leadership skills. 
-->

# UNIVERSITY GOVERNANCE AND SERVICE

```{r, include = FALSE, message = FALSE}
dat_service <- readRDS("data/service.RDS")

uni_service <- filter(dat_service, setting %in% c("university", "library"))
dat_service <- anti_join(dat_service, uni_service)
```

## University

```{r}
print_service(uni_service, sublocale = "university")
```

## College

```{r}
print_service(uni_service, sublocale = "college")
```

## Department/Center

```{r}
print_service(uni_service, sublocale = "department")
```

# CONSULTATIONS OUTSIDE THE UNIVERSITY

None

# EDITOR OF SCHOLARLY JOURNALS, SERVICE OR EDITORIAL ADVISORY BOARDS, REVIEWER FOR SCHOLARLY JOURNALS

## Editor

```{r, message = FALSE}
dat_editor <- filter(dat_service, stringr::str_detect(dat_service$role, "editor"))
dat_service <- anti_join(dat_service, dat_editor)

dat_editor %>%
    format_service() %>%
    print_data(prefix = "* ", sep = "\n\n")
```

## Editorial Advisory Boards

None

## Reviewer for Scholarly Journal

```{r}
dat_reviews <- readRDS("data/reviews.RDS")

dat_reviews %>%
    format_reviews() %>%
    print_data(prefix = "* ", sep = "\n\n", 
               empty_message = "None\n")
    
```

## Book Manuscripts Reviewed

None

# INTERNATIONAL ACTIVITIES

Reproducibility is a multi-faceted issue that presents a multitude of challenges and possible solutions. In engaging with international collaborators, stakeholders, and audiences, I am able to both share with and learn from a diverse set of backgrounds and experiences that enhance the impact of my work. This is particularly relevant when interacting with reproducibility and open science groups outside the US and thinking about what kinds of multi-institutional or multi-sector partnerships can shift research practices in the US, Florida, the University, and more local settings. Conversely, my service to international communities and professional organizations enables me to stay on the forefront of advances and practices in the areas of research reproducibility and open research.

# EXTENSION PROGRAMS (for IFAS only)

N/A

# CLINICAL SERVICE, CLINICAL ACTIVITIES, OR CLINICAL PORTFOLIO

N/A

# SERVICE TO SCHOOLS

None

# MEMBERSHIP AND ACTIVITIES IN THE PROFESSION

## MEMBERSHIPS

```{r, include = FALSE, message = FALSE}
memberships <- filter(dat_service, activity == "n")
```

### International

```{r}
print_memberships(memberships, locale = "international")
```

### National

```{r}
print_memberships(memberships, locale = "national")
```

### Regional

```{r}
print_memberships(memberships, locale = "regional")
```

### State

```{r}
print_memberships(memberships, locale = "state")
```

### Local

```{r}
print_memberships(memberships, locale = "local")
```

## ACTIVITIES IN THE PROFESSION

```{r, include = FALSE, message = FALSE}
activities <- filter(dat_service, activity == "y")
```

### International

```{r}
activities %>%
    filter(locale == "international") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### National

```{r}
activities %>%
    filter(locale == "national") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### Regional

```{r}
activities %>%
    filter(locale == "regional") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### State

```{r}
activities %>%
    filter(locale == "state") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### Local

```{r}
activities %>%
    filter(locale == "local") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

# HONORS

```{r, include = FALSE}
awards <- readRDS("data/awards.RDS")
```

## International

```{r}
print_awards(awards, locale = "international")
```

## National

```{r}
print_awards(awards, locale = "national")
```

## Regional

```{r}
print_awards(awards, locale = "regional")
```

## State

```{r}
print_awards(awards, locale = "state")
```

## Local

```{r}
print_awards(awards, locale = "local")
```

# CHAIR’S LETTER

# DEAN’S LETTER

# SAMPLE LETTER TO EVALUATORS

# BIO-SKETCHES OF INDIVIDUALS WRITING SOLICITED LETTERS OF EVALUATION and LETTERS OF EVALUATION

<!-- MRT: Although you won’t be asking for letters, this is a great time to think about who you might ask. You could list them here with a short explanation as to why. -->


# COPIES OF THE LAST FIVE ANNUAL LETTERS OF EVALUATION

# FURTHER INFORMATION

## Submitted Talks

```{r}
print_talks(dat_talks, locale = NULL, submitted = TRUE)
```

## Submitted Manuscripts

```{r}
dat_research <- readRDS("data/research.RDS")
pubs <- filter(dat_research, status %in% c("in review", "submitted"))

pubs %>%
    format_research("paper", my_bib) %>%
    remove_IN() %>%
    underline_first_author() %>%
    format_author() %>%
    print_data(prefix = "", sep = "\n\n<br />\n\n", 
               empty_message = "None\n")
```

