---
output: 
  word_document:
    reference_docx: "packet_styles.docx"
---

```{r setup, include = FALSE}
library(tidyverse)
library(lubridate)
library(googlesheets4)
library(RefManageR)
library(activityReporteR)
library(flextable)

report_start_date <- as.Date("2020-05-01")
report_end_date <- as.Date("2100-01-01")

data_gs_url <- "https://docs.google.com/spreadsheets/d/11XRsF-MupYcnZlykUe6YHAGe1A16CxJyq9nT3oSbDeg/edit#gid=0"
gs4_auth("haoye@ufl.edu")

data_bib_file <- "my_lib.bib"
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           cite.style = "apa",
           style = "markdown",
           max.names = Inf, 
           hyperlink = FALSE,
           dashed = FALSE, 
           use.misc.default.format = TRUE)
my_bib <- ReadBib(data_bib_file, check = FALSE)

set_flextable_defaults(
    font.family = "Times New Roman", 
    font.size = 11, 
    border.color = "black", 
    table.layout = "fixed", 
    padding.top = 3, padding.bottom = 1
)

source("R/download_gs_data.R")
source("R/format_data.R")
source("R/format_word_tables.R")
source("R/print_data.R")

knitr::opts_chunk$set(echo = FALSE, results = "asis", message = FALSE)
```

```{r check data sources}
data_files <- c("data/degrees.RDS", 
                "data/jobs.RDS", 
                "data/effort_perc.RDS", 
                "data/teaching_summary.RDS", 
                "data/teaching_evals.RDS", 
                "data/course_info.RDS", 
                "data/grad_committees.RDS",
                "data/teaching.RDS", 
                "data/research.RDS",
                "data/videos.RDS", 
                "data/grants.RDS", 
                "data/service.RDS", 
                "data/reviews.RDS", 
                "data/awards.RDS", 
                "data/talks.RDS")
data_files_found <- file.exists(here::here(data_files))
if (!all(data_files_found))
{
    missing_files <- paste0("file '", 
                            data_files[!data_files_found], 
                            "' not found")
    vapply(missing_files, warning, "", call. = FALSE)
}
```

# NOMINEE INFORMATION COVER SHEET 

<!--

The cover sheet automatically gets added after the PDF is uploaded into UF's OPT system.
-->

# BRIEF DESCRIPTION OF JOB DUTIES 

<!-- Briefly describe your assigned duties and responsibilities. Provide context for these responsibilities (ie. the relevance and importance to your discipline and UF -->

As the reproducibility librarian of the University of Florida George A. Smathers Libraries, I am responsible for developing and executing a strategy for trans-disciplinary research reproducibility and open science for the entire campus community. 
Research reproducibility and open science encompass a variety of practices, including information retrieval/storage, data and computational workflows, responsible conduct of research, and open scholarship broadly defined (e.g., open access, publishing data and code, preprints). 
I also serve as the liaison librarian to several departments and programs in the College of Medicine and College of Public Health and Health Professions: Biostatistics, Health Outcomes and Biomedical Informatics, and the Graduate Program in Biomedical Sciences. 
My activities include providing information consultation services, designing and teaching workshops in research reproducibility, collaborating with other faculty in course-integrated instruction, and participating in broader teaching initiatives in the Smathers Libraries. 
In addition, I carry out and support special projects and programs related to the overall mission of the Academic Research Consulting & Services (ARCS) department, including the Student HiPerGator Sponsorship program, Artificial Intelligence, and Research Integrity. 
My scholarship is impactful and innovative in identifying pathways to make research more open and reproducible. 
My work specifically explores new modes and models for research and examines interventions that shift existing practices, such as through instruction, technical infrastructure, and sociocultural incentives. 
As faculty of a leading public university, I engage in service and leadership both internally through university and library committees, and externally at national and international levels. 
My service activities focus especially on areas that complement or directly relate to promoting research reproducibility. 

## Impact of COVID pandemic on Job Duties
<!-- In this optional section faculty may provide a statement regarding the impact of the COVID-19 pandemic on the nominee’s professional life -- up to 500 words. This statement should explain how the nominee adjusted/compensated for pandemic-related difficulties impacting their research, teaching, clinics, extension or service. Please see http://aa.ufl.edu/policies/tenure-and-promotion-information/ for more details. This was a new section beginning in 2021. -->

The COVID pandemic had a substantial and indeterminate effect on my professional responsibilities. In between my hire and my start in May 2020, the university campus closed. On top of the challenges of starting a new position, there were many obstacles resulting from operating in unprecedented circumstances. The overall environment and its uncertainties increased the difficulty of planning events, performing in-person outreach, and connecting with both my liaison departments and broader units on campus.

I made use of my existing experience in lesson development and delivering training online to offer workshops online through the Zoom platform. This had the dual advantage of establishing a permanent, online record of my lesson content, as well as expanding the accessibility of my instruction to anyone, instead of being limited to in-person attendance.

Although the campus re-opened to employees in Summer 2021, there was still a great deal of uncertainty through the Fall 2021 semester, with many classes being offered hybrid and many events remaining virtual. This resulted in delays for certain activities--for my IMLS-funded project (see Section 13 for more details), I led my project team to plan in-person meeting, not knowing what future COVID transmission levels or safety measures would be feasible or acceptable to attendees.

# AREAS OF SPECIALIZATION

* **Reproducibility**: promoting research practices that support "reproducibility" (the ability to generate identical or equivalent results to that of an existing publication using the same dataset and analysis procedures), encompassing data management, sharing intermediate products such as data and code, and accurate and rigorous reporting of statistical analyses.

* **Open research**: A philosophy of radical openness and transparency that may be applied to all facets of research. The open research ethos recognizes that many research problems are complex and thus benefit from teams of researchers working collectively and sharing information (e.g., open access and data sharing commitments for COVID-19 research)

* **Liaison librarianship**: supporting students, staff, and faculty in the health sciences through various activities such as: expert literature searching, teaching best practices in information searching and retrieval, developing relevant and appropriate library resources and collections, 

* **Diversity, equity, and inclusion**: cultivating environments and systems that are intentionally welcoming of individuals from all backgrounds, including historically and presently oppressed group identities, such as race, nationality, gender, sexuality, disability status, etc. 

# EFFORT REPORTED SINCE UF EMPLOYMENT

```{r}
df <- readRDS("data/effort_perc.RDS")

# start table at `first_term`
first_term <- "Spring 2020"
last_row <- which(df[,1] == first_term)
if (length(last_row) == 1)
{
    df <- df[seq(from = 1, to = last_row), ]
}

format_effort_perc(df, dept_name = "Academic Research Consulting & Services")
```

<br />

# EDUCATIONAL BACKGROUND

```{r, message = FALSE}
dat_degrees <- readRDS("data/degrees.RDS")
dat_degrees %>%
    mutate(Year = as.character(year(as.Date(Date)))) %>%
    select(-Date) %>%
    arrange(desc(Year)) %>%
    flextable() %>%
    set_table_properties(layout = "autofit") %>%
    theme_box() %>% 
    align(align = "center", part = "header")
```

<br />

# EMPLOYMENT

```{r, message = FALSE}
dat_jobs <- readRDS("data/jobs.RDS")
dat_jobs %>%
    format_jobs() %>%
    flextable() %>%
    set_table_properties(layout = "autofit") %>%
    theme_box() %>% 
    align(align = "center", part = "header")
```

<br />

# YEAR TENURE/PERMANENT STATUS WAS AWARDED BY UNIVERSITY OF FLORIDA

N/A

# TENURE AND PROMOTION CRITERIA

# TEACHING, ADVISING, AND INSTRUCTIONAL ACCOMPLISHMENTS

```{r, include = FALSE}
dat_teaching <- readRDS("data/teaching.RDS")
```

*NOTE: To support the teaching and research missions of the University, Library faculty are assigned to varying degrees to perform public, technical, archival, and administrative functions. These primary activities are referred to in the Libraries' T&P Criteria as "Professional Responsibilities" rather than "Teaching" to better reflect the unique and specialized activities in which Library faculty engage.*

```{r, include = FALSE}
carpentries_instructor_trainings <- filter(dat_teaching, 
                                           str_detect(title, "Carpentries Instructor Training"))

standalone_stats <- filter(dat_teaching, 
                           type == "standalone")
standalone_sessions <- NROW(standalone_stats)
standalone_attendees <- sum(as.numeric(standalone_stats$num_attendees))

dat_research <- readRDS("data/research.RDS")
oer_works <- filter(dat_research, type %in% c("OER")) %>%
    join_zenodo_stats()

refstats <- read_redcap_data(db = "refstats", 
                             report_start_date, report_end_date) %>%
    mutate(consultation = recode(consultation, `1` = "yes", `2` = "no"))

searches <- read_redcap_data(db = "searches", 
                             report_start_date, report_end_date, 
                             date_cols = "date_rec")

num_refstats <- NROW(refstats)
num_consults <- sum(refstats$consultation == "yes")
num_searches <- NROW(searches)

num_videos <- readRDS("data/videos.RDS") %>% NROW()
```

As the reproducibility librarian, I provide training and instruction in reproducibility and replicability to researchers.
Briefly, a study is **reproducible** if an independent researcher can perform an identical analysis on the same dataset, and achieve equivalent results; a **replication study** collects new data and follows the same procedures to test if the original results generalize.
Both reproducibility and replicability relate to the reliability of research results, and are thus important for early career researchers to adopt.

My instructional reach spans the UF community.
I co-teach a for-credit course with colleagues in HSCL and ARCS, "GMS 5909: Finding Biomedical Research Information and Communicating Science", introducing reproducibility as an essential facet of the research process. While this graduate-level course was originally created for students in the health sciences, it has attracted students from throughout campus.
I reach multiple research disciplines through guest lectures and course-integrated instruction---invited instruction for classes where I am not the instructor of record, with associated course assignments.
For example, I regularly lead a session in "GMS 7877: Responsible Conduct of Biomedical Research", discussing reproducibility and its relationship with research integrity.
I provide guest lectures for courses in diverse departments and programs across UF, such as Biomedical Engineering, Latin American Studies, Entomology & Nemotology, the UF Office of Research's Research Integrity Summer Seminar Series, and a Course-Based Undergraduate Research Experience in Genomics.
This broad influence reflects the growing awareness of the importance of reproducibility, and my ability to provide effective instruction to different disciplines.

However, because research is so varied, there are limitations to these forms of instruction. 
Consequently, I have developed and teach an array of standalone workshops that are not related to any specific class, program, or unit, but are available to the entire university community.
To make these workshops relevant and engaging, I feature practical skills that can be implemented immediately, along with follow-up resources for further training and practice.
To maximize reach, I offer these workshops virtually through Zoom, provide recordings to registered attendees, and share the instructional materials online.
Nevertheless, learners still find benefits to attending "live", as seen in my total count of `r standalone_attendees` attendees across `r standalone_sessions` sessions.
To expand the impact of my educational content to students and researchers beyond the University of Florida, I publish and disseminate my materials as open educational resources on the Zenodo repository; collectively these have `r sum(oer_works$views)` views and `r sum(oer_works$downloads)` downloads.

My ability to provide effective instruction is recognized beyond UF, and has been sought out by organizations such as the NIH Office of Data Science Strategy and the African Society for Bioinformatics and Computational Biology.
For both organizations, I have been an invited instructor in codeathon events, where groups of participants work closely together on a project over 2-5 days.
I teach skills and techniques to help the teams in their project; these tutorials are positively received, with measured uptake of new practices during the events and invitations to return for future events.

In addition to teaching directly, I enhance my instructional impact by developing other teachers.
In summer 2021, I completed trainer training for The Carpentries, an international non-profit organization that develops and teaches practical and reproducible coding and data science skills to researchers.
I can now train new instructors, sustaining both The Carpentries global organization, as well as the local chapter at UF (the UF Carpentries Club).
To date, I have taught `r NROW(carpentries_instructor_trainings)` instructor training sessions to a total of `r sum(as.numeric(carpentries_instructor_trainings$num_attendees))` new instructors. 

My day-to-day responsibilities include creating and sustaining programs and services.
This includes the HiPerGator Student Sponsorship program, which provides high-performance and/or secure computing environments for student research projects that lack other funding and developing Artificial Intelligence trainings for the UF libraries.
I also provide reference services to my liaison departments - Health Outcomes and Biomedical Informatics, Biostatistics (through December 2022), and the Graduate Program in Biomedical Sciences - and general users of the Health Science Center Library in Gainesville.
These have resulted in `r num_refstats + num_searches` interactions, including `r num_consults` in-depth consultations and `r num_searches` literature searches.

In collaboration with the UF Norman Fixel Institute for Neurological Diseases, I organize the Rigor and Reproducibility Seminar Series, funded by a T32 training grant to PIs Dawn Bowers and David Vaillancourt. This series has hosted `r num_videos` guest speakers on topics in research integrity, reproducibility, and open science - https://uf-repro.github.io/movementdisorders-seminar/ .
<!--The seminar series has been well-received, both with audiences at UF, and with representatives from the NIH, who have communicated interest in implementing the idea more broadly to support research integrity efforts. -->

# TEACHING EVALUATIONS

## UF Teaching Evaluations

**Summary Table**

<br />

```{r}
df <- readRDS("data/teaching_summary.RDS") %>%
    remove_empty_rows()
format_teaching_summary(df)
```

<br />

```{r}
df <- readRDS("data/teaching_evals.RDS")
course_info <- readRDS("data/course_info.RDS")
format_teaching_eval(df, course_info)
```

**Additional Classes**

The majority of my instruction occurs in single session or multi-session workshops that receive no evaluations. These activities are divided into the following categories:

### Course-Integrated Instruction

```{r}
dat_teaching %>%
    filter(type == "course-integrated") %>%
    dplyr::mutate(other_instructor = ifelse(is.na(other_instructor), "", 
                                            glue::glue("co-instructor with {other_instructor}, ")),
                  print_header = glue::glue('**{course_id}: {title}** - *{session}*, {date}, {other_instructor}'),
                  print_instructor = glue::glue("  \nCourse Instructor: {instructor}"),
                  to_print = glue::glue("{print_header}  \n{print_instructor}\n", .trim = FALSE)) %>%
    dplyr::select(date, to_print) %>%
    print_data()
```

### Standalone Library Workshops

```{r}
dat_teaching %>%
    filter(type == "standalone") %>%
    group_by(title) %>%
    summarize(n = n(), 
              date = min(date)) %>%
    mutate(session_line = glue::glue("{n} {ifelse(n > 1, 'sessions', 'session')}"), 
           to_print = glue::glue('*{title}*, {session_line} since {year(date)}')) %>%
    print_data()
```

### Other Instruction

```{r}
dat_teaching %>%
    filter(type == "other", 
           is.na(outreach) | outreach == "n") %>%
    mutate(title = ifelse(is.na(session), title, glue::glue("{title}: {session}")), 
           to_print = glue::glue('*{title}*, {event_info}, {date}')) %>%
    print_data()
```

## Peer assessments

None

# EDUCATIONAL PORTFOLIO (if applicable)

N/A

# GRADUATE COMMITTEE ACTIVITIES

```{r}
df <- readRDS("data/grad_committees.RDS") %>%
    remove_empty_rows()

format_grad_committee(df)
```

# CONTRIBUTION TO DISCIPLINE/RESEARCH NARRATIVE

```{r}
dat_research <- readRDS("data/research.RDS")
oer_works <- filter(dat_research, type %in% c("OER")) %>%
    join_zenodo_stats()
```

There is growing interest and awareness of issues around replicability/reproducibility, and concomitant policies from institutions and funders.
My work empowers researchers with the tools and training to navigate this changing landscape, investigates the effectiveness of different mechanisms for shifting practices, and addresses the structures that perpetuate barriers to equity and inclusion in the research ecosystem.

<!-- Reproducibility and replicability refer to the trustworthiness and robustness of research results. Following the definitions adopted by the National Academies of Sciences, Engineering, and Medicine, a study is **reproducible** if an independent researcher can perform an identical analysis on the same dataset, and achieve equivalent results; a **replication study** involves collecting new data and following the same procedures to test if the results of the initial study generalize. -->

*Reproducibility Training*

Because there are a multitude of factors that may cause irreproducibility, there is no consensus on the best approach to promote reproducibility.
Thus, I engage with other researchers and instructors to discuss and evaluate the effectiveness of different approaches to reproducibility training.
Following the "Research Reproducibility 2020: Educating for Reproducibility" virtual conference that I co-organized, I and the other members of the organizational team wrote a synthesis of the themes, published in the _Journal of Statistics and Data Science Education_.
I also co-authored a case study of different approaches to reproducibility training, accepted for publication in the _Journal of the Medical Library Association_

As a recognized expert, I was invited to attend a workshop hosted by the NIH National Institute of Neurological Disorders and Stroke in May 2022 on "Catalyzing Communities of Research Rigor Champions".
This event brought together leading researchers and institutional representatives to discuss how shifting the way research is done requires not just incentives, mandates, and education, but socio-cultural factors, such as local communities of practice.

*Open Science^[Although "open science" is the most common term, many aspects apply to research fields that are not considered part of science. I use "open science" here to refer broadly to "open research" or "open scholarship".] Practices*

One of the common pathways to improve reproducibility is to increase openness and transparency in research.
This includes actions that are already established, such as sharing publications via open access, as well as emergent, such as sharing data, analysis code, and pre-registered study protocols.
Some of my work explores these boundaries, to provide better guidance to researchers, as well as shape research practice more broadly.

To explore the challenges and solutions in bringing openness and transparency to grant proposals, I am the PI on the project "Planning for Open Grants: Fostering a Transparent and Accessible National Research Proposal Infrastructure", funded by the Institute for Museum and Library Services.
This project engages with stakeholders across research sectors, including researchers, administrators, funders, and technologists.
Outputs from the project include conference talks (1 completed, and 1 proposed) and publications (1 accepted for full submission to the _College & Research Libraries_ topical issue on "Open and Equitable Scholarly Communications"). 

With growing interest in open science, high-level organizations have created or plan to create implementation guidelines. 
In response to the 2022 call from UNESCO for feedback on the "UNESCO Recommendation on Open Science", I co-authored a commentary to provide input on several key areas, "Open Life Science (OLS) response to UNESCO global call for best practices in open science".
This collaboration brought together our lived experience and expertise in open science education and open science communities to inform policy at the highest levels.

*Equity and Inclusion*

Open research is commonly considered to include aspects such as bringing research to the public, through open access and citizen science projects that invite the public to participate in research.
This perspective can also be brought to bear on academic research systems and their practices in equity and inclusion.
My work in this area includes advocating for more equality in job recognition of contributions to research.
For example, I co-led a paper on the need for better career support for research support specialists, who are not typically acknowledged as researchers, "A manifesto for rewarding and recognising Team Infrastructure Roles", submitted to the _Journal of Trial and Error_.

I also seek to cultivate environments that are more inclusive and welcoming.
With my expertise in allyship skills and providing instruction in allyship skills, I co-authored a paper that provides an introduction to these skills and practices, "An Introduction to Ally Skills for Natural History Collections Professionals".

# CREATIVE WORKS OR ACTIVITIES

## Open Educational Resources

In keeping with my principles of opening up scholarly and teaching work, I share the contents of my standalone workshops as Open Educational Resources.

```{r, results = "asis"}
oer_works %>% 
    format_zenodo_stats() %>%
    format_oer_works() %>% 
    print_data(prefix = "* ", sep = "\n\n", 
               empty_message = "None\n")
```

## Video recordings for "Rigor and Reproducibility Seminar Series"

```{r}
dat_videos <- readRDS("data/videos.RDS")
video_summary <- dat_videos %>%
    summarize(first_date = min(date), 
              last_date = max(date), 
              count = n())
```

This ongoing seminar series is jointly hosted by the UF Norman Fixel Institute for Neurological Diseases and the UF Health Science Center Libraries. Since the first seminar on `r strftime(video_summary$first_date, "%B %d, %Y")`, I have organized and moderated a total of `r video_summary$count` seminars. Recordings of all the seminars are linked on https://uf-repro.github.io/movementdisorders-seminar/. 

## Libguides

* Research Reproducibility and Open Science - https://guides.uflib.ufl.edu/reproducibility  
2613 views between 2020-05-01 and 2022-11-04
* Health Outcomes and Biomedical Informatics - https://guides.uflib.ufl.edu/hobi  
286 views between 2020-05-01 and 2022-11-04
* CoM Graduate Program in Biomedical Sciences - https://guides.uflib.ufl.edu/BMS  
17 views between 2020-05-01 and 2022-11-04
* Biostatistics - https://guides.uflib.ufl.edu/biostats  
68 views between 2020-05-01 and 2022-11-04


<!-- MRT: If you have LibGuides they would go here and would include date of creation, date of update, and number of uses. For your creative works below, would be helpful to have dates and usage if that is possible. -->

## Other Creative Works

```{r, results = "asis"}
dat_research <- readRDS("data/research.RDS")
works <- filter(dat_research, type %in% c("other", "software", "preprint", "podcast")) %>%
    join_zenodo_stats()

works %>% 
    format_zenodo_stats() %>%
    join_bib_data(my_bib) %>%
#    format_research_other(my_bib, zenodo_text) %>%
    mutate(to_print = glue::glue("{to_print} {zenodo_text}")) %>% 
    underline_first_author() %>%
    format_author() %>%
    print_data(prefix = "* ", sep = "\n\n", 
               empty_message = "None\n")
```

# PATENTS AND COPYRIGHTS

None

# PUBLICATIONS

## Books, Sole Author
<!-- (Title, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Books, Co-authored
<!-- (Co-author(s), Title, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Books, Edited
<!-- (Editor, Co-editor(s), Title, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Books, Contributor of Chapter(s)
<!-- (Author, Co-author(s), Title of Book and Chapter, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Monographs
<!-- (Author, Co-author(s), Title, Series of Volume, if applicable, Publisher, Place of Publication, Date, Inclusive Pages) -->
None

## Refereed Publications
<!-- (Author, Co-author(s), Title, Name of Journal or Publication, Volume, Date, Inclusive Pages) -->

```{r, results = "asis"}
dat_research <- readRDS("data/research.RDS")
pubs <- filter(dat_research, status %in% c("published", "forthcoming"))

pubs %>%
    format_research("paper", my_bib) %>%
    remove_IN() %>%
    underline_first_author() %>%
    format_author() %>%
    print_data(prefix = "", sep = "\n\n<br />\n\n", 
               empty_message = "None\n")
```

## Non-refereed Publications
<!-- Author, Co-author(s), Title, Name of Journal, Bulletin, Circular, or other Publication, Volume, Date, Inclusive Pages -->
None

## Bibliographies/Catalogs
<!-- Author, Co-author(s), Title, Publisher, Place of Publication, Date, Inclusive Pages -->
None

## Abstracts
<!-- Author, Co-author(s), Title, Name of Journal or Publication, Volume, Date, Inclusive Pages -->
None

## Reviews
<!-- Author, Co-author(s), Title and Author of Work Reviewed, Where Review was Published, Date, Inclusive Pages -->
None

## Miscellaneous
<!-- Author, Co-author(s), Title, Source of Publication, Date, Inclusive Pages -->

# LECTURES, SPEECHES, POSTERS PRESENTED AT PROFESSIONAL CONFERENCES/SEMINARS

```{r}
dat_talks <- readRDS("data/talks.RDS") %>%
    filter(type == "talk") %>%
    replace_na(list(invited = "n", location = ""))

outreach_instruction <- dat_teaching %>%
    filter(type == "other", outreach == "y")

```

## International

```{r}
combine_talks_and_outreach(dat_talks, outreach_instruction, locale = "international")
```

## National

```{r}
combine_talks_and_outreach(dat_talks, outreach_instruction, locale = "national")
```

## Regional

```{r}
combine_talks_and_outreach(dat_talks, outreach_instruction, locale = "regional")
```

## State

```{r}
combine_talks_and_outreach(dat_talks, outreach_instruction, locale = "state")
```

## Local

```{r}
combine_talks_and_outreach(dat_talks, outreach_instruction, locale = "local")
```

# SPONSORED PROJECTS

```{r, include = FALSE}
start_year <- year(report_start_date)
end_year <- min(year(report_end_date), year(Sys.Date()))
```

## Funded

### List of Funded Grants

```{r, include = FALSE}
dat_grants <- readRDS("data/grants.RDS")
```

#### List of Funding - Internal `r start_year` to `r end_year`

```{r, message = FALSE, results = "asis"}
grants <- filter(dat_grants, funder_loc == "internal")

if (NROW(grants) > 0)
{
    grants %>%
        format_grants_table() %>%
        print_grants_table()
} else {
    cat("None")
}
```

#### List of Funding - External `r start_year` to `r end_year`

```{r, message = FALSE, results = "asis"}
grants <-  filter(dat_grants, funder_loc == "external")

if (NROW(grants) > 0)
{
    grants %>%
        format_grants_table() %>%
        print_grants_table()
}
```

<br />

### Summary of Grant Funding

```{r}
dat <- tibble(ROLE = c("Principal Investigator", "Co-Principal Investigator", "Investigator", "Senior Personnel", "Sponsor of Junior Faculty", "Totals"), 
                  TOTAL = c(99833, 0, 8697, 0, 0, 108530), 
                  `Direct Costs` = c(75289, 0, 6675, 0, 0, 81964), 
                  `Indirect Costs` = c(24544, 0, 2022, 0, 0, 26566))

dat %>%
    flextable() %>%
    set_table_properties(layout = "autofit") %>%
    theme_box() %>%
    align(align = "center", part = "header") %>%
    align(align = "center", i = 6, j = 1)

```

### Short Narrative of Grant Funding

**Planning for Open Grants: Fostering a Transparent and Accessible National Research Proposal Infrastructure** (ongoing)

The funds for this grant support work on a planning project to explore the social and technical issues around an open repository, including hiring two graduate student research fellows, stipends for an external advisory board, and conference travel. As the PI, I lead the project team, coordinate the activities, and supervise the student hires.

**Supplement: GatorSTAR: A New MARC** (ongoing)

The funds for this grant support salaries for team members and the creation and implementation of training modules to educate students on how to share data following the FAIR (Findable Accessible Interoperable Reusable) guidelines. As a Co-Investigator for this project, I co-create the materials and assist with the evaluation of the lesson effectiveness.

**Educating for Reproducibility: Pathways to Integrity**

The funds for this grant supported salaries and the hosting of a virtual conference on education in reproducibility across different research disciplines and career stages. As a Co-Investigator for this project, I was a co-planner for the conference, and facilitated the event itself by moderating and hosting sessions.

# SERVICE NARRATIVE 

<!-- As with my research and teaching, the overarching goal of my service work is to improve research practices in the service of reproducibility and openness. Because service work does not often directly affect these qualities, my activities generally involve cultivating resources, communities, and infrastructure to support the research activities of others. -->

With my recognized expertise in data science and open science, I have been invited to evaluate funding proposals for several international organizations.
In 2020, I began serving on the Event Fund Selection Committee for _Code for Science & Society_, a nonprofit organization that works to "advance the power of data to improve the social and economic lives of all people through public education, scientific research, and technology development and deployment".
With the other committee members, I evaluated and recommended for funding, events that build inclusive data science communities. Through 3 rounds of awards, we supported 37 events, representing 27 countries and 6 continents.
<!--Before stepping down in Spring 2022, I provided input on the application and review process.-->
In 2021, I was an invited grant reviewer for the Wellcome Trust - Data for Science and Health Award, providing evaluation of a research proposal in the area of ecological modeling and data science.

Some of my most impactful work is in organizing communities to work together.
As the elected chair of the Medical Library Association's Data Caucus, a group comprising over 200 data librarians, I create capacity for collaborations and resource-sharing.
Out of this community, I established an ongoing working group that creates guidance materials for the new NIH Data Management and Sharing Policy.
This new policy goes into effect in January 2023 and mandates Data Management and Sharing Plans to accompany all funding proposals, to maximize data sharing and re-use.
By leveraging collective effort, the working group reduces redundancy among those of us who support researchers with data services, and also helps to ensure more comprehensive guidance.
This group has created several public resources (https://osf.io/uadxr/) that are being used and re-shared (for example, by the Network of the National Library of Medicine - https://www.nnlm.gov/guides/nnlm-toolkit-nih-data-management-and-sharing-policy ).
To support honoraria for contributors and meeting facilitators, I successfully requested funding from professional organizations (RDAP - Research Data Access and Preservation Association, and the Network of the National Library of Medicine National Center for Data Services).

As an associate editor at _Methods for Ecology & Evolution_, I handle approximately 6 manuscripts a year: identifying and recruiting peer reviewers, reading the manuscript and its reviews, and making a recommendation to the senior editors.
This work is rewarding in giving me the opportunity to guide authors in improving their writing, and to encourage early career authors, including students.
In September 2022, I was invited to join the editorial board at _Ecology_ as an editor of the "Data Paper" submission format.
In this new position, I am refining the standards to enhance data re-use, while streamlining the submission process.

As chair of the UF Libraries Open Access Committee, I lead the group in supporting open access publishing at the university.
These activities include: creating outreach messaging, promoting of read-and-publish initiatives, and hosting a discussion panel for Open Access Week in October 2022.
To bring further transparency to our decision making, we are preparing to release our evaluation rubric for open access initiatives.
This will promote engagement with the broader community of open access advocates across institutions and research sectors.

Many of my service activities revolve around promoting an equitable and inclusive environment.
I serve as a member of the Code of Conduct Committee for _Reproducibility for Everyone_, a global community that shares instructional modules and teaches workshops on reproducibility.
In support of this work, I have received training in Code of Conduct enforcement, and co-developed, with the rest of the committee, detailed procedures for documenting and responding to code of conduct incidents, should they arise.
I apply my DEI experiences and training at the University of Florida through the design of inclusive events for student-facing committees (e.g., UF Libraries Student Engagement Committee, UF Libraries Fall Fest Committee, HSCL Diversity, Equity, and Inclusion Team).
In particular, I strive to make sure events are broadly accessible, such as for online students who are not able to participate in in-person events in Gainesville.

I have served on 4 search committees for the UF Libraries (1 ongoing), including one as chair. This work combines both my expertise in research support as a member of the ARCS department and my experience in diversity, equity, and inclusion: 3 of the 4 searches have been for ARCS department members, and in multiple committees, I have acted as the DEI search advocate. In the latter role, I have additional responsibilities such as promoting the position to individuals from diverse backgrounds, ensuring the search is fair and equitable, and evaluating candidates on their ability to contribute to the DEI mission of the libraries and the university.

<!-- 
In addition to promoting reproducibility and open research practices through training, I strive to create environments where better practices are normalized and encouraged.  and providing suitable resources that lower the burden to change.


I continually seek out opportunities to enhance the impact of my service, including developing and deploying teaching or leadership skills. 
-->

# UNIVERSITY GOVERNANCE AND SERVICE

```{r, include = FALSE, message = FALSE}
dat_service <- readRDS("data/service.RDS")

uni_service <- filter(dat_service, setting %in% c("university", "library"))
dat_service <- anti_join(dat_service, uni_service)
```

## University

```{r}
print_service(uni_service, sublocale = "university")
```

## College

```{r}
print_service(uni_service, sublocale = "college")
```

## Department/Center

```{r}
print_service(uni_service, sublocale = "department")
```

# CONSULTATIONS OUTSIDE THE UNIVERSITY

None

# EDITOR OF SCHOLARLY JOURNALS, SERVICE OR EDITORIAL ADVISORY BOARDS, REVIEWER FOR SCHOLARLY JOURNALS

## Editor

```{r, message = FALSE}
dat_editor <- filter(dat_service, stringr::str_detect(dat_service$role, "editor"))
dat_service <- anti_join(dat_service, dat_editor)

dat_editor %>%
    format_service() %>%
    print_data(prefix = "* ", sep = "\n\n")
```

## Editorial Advisory Boards

None

## Reviewer for Scholarly Journal

```{r}
dat_reviews <- readRDS("data/reviews.RDS")

dat_reviews %>%
    format_reviews() %>%
    print_data(prefix = "* ", sep = "\n\n", 
               empty_message = "None\n")
    
```

## Book Manuscripts Reviewed

None

# INTERNATIONAL ACTIVITIES

<!-- I’d use this space as an opportunity to reiterate all of those international invitations that you’ve received. I do think I would list them in the section on presentations (rather than instruction), and just allude back to them here a little more obviously than you have done. 

For this section I have the same comment as last time - this section can be a lot more robust if you tie directly to some of the international presentation invitations you've listed elsewhere.
-->

Reproducibility is a multi-faceted issue that presents a multitude of challenges and possible solutions.
In engaging with international collaborators, stakeholders, and audiences, I am able to both share with and learn from a diverse set of backgrounds and experiences that enhance the impact of my work.
This is particularly relevant when interacting with reproducibility and open science groups outside the US.
For example, I have been invited to present on or provide instruction in topics such as version control, packaging research software, licensing, and DEI at seminars and events organized by international organizations (e.g., the African Society for Bioinformatics and Computational Biology, Open Life Science).
My connection with international researchers and instructors also creates opportunities to reflect on, implement, or adapt training practices for use at the University of Florida (e.g., the international conference "Research Reproducibility 2020: Educating for Reproducibility").
I also collaborate with multi-national, cross-institution groups to discuss policy issues related to reproducibility and research support (e.g., commentary on the "UNESCO Recommendation on Open Science" and the submitted manuscript "A manifesto for rewarding and recognising Team Infrastructure Roles").
Overall, my participation in and service to international communities and professional organizations enables me to stay on the forefront of advances and practices in the areas of research reproducibility and open research.

# EXTENSION PROGRAMS (for IFAS only)

N/A

# CLINICAL SERVICE, CLINICAL ACTIVITIES, OR CLINICAL PORTFOLIO

N/A

# SERVICE TO SCHOOLS

None

# MEMBERSHIP AND ACTIVITIES IN THE PROFESSION

## MEMBERSHIPS

```{r, include = FALSE, message = FALSE}
memberships <- filter(dat_service, activity == "n")
```

### International

```{r}
print_memberships(memberships, locale = "international")
```

### National

```{r}
print_memberships(memberships, locale = "national")
```

### Regional

```{r}
print_memberships(memberships, locale = "regional")
```

### State

```{r}
print_memberships(memberships, locale = "state")
```

### Local

```{r}
print_memberships(memberships, locale = "local")
```

## ACTIVITIES IN THE PROFESSION

```{r, include = FALSE, message = FALSE}
activities <- filter(dat_service, activity == "y")
```

### International

```{r}
activities %>%
    filter(locale == "international") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### National

```{r}
activities %>%
    filter(locale == "national") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### Regional

```{r}
activities %>%
    filter(locale == "regional") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### State

```{r}
activities %>%
    filter(locale == "state") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

### Local

```{r}
activities %>%
    filter(locale == "local") %>%
    format_service() %>%
    print_data(prefix = "", sep = "\n\n", 
               empty_message = "None\n")
```

# HONORS

```{r, include = FALSE}
awards <- readRDS("data/awards.RDS")
```

## International

```{r}
print_awards(awards, locale = "international")
```

## National

```{r}
print_awards(awards, locale = "national")
```

## Regional

```{r}
print_awards(awards, locale = "regional")
```

## State

```{r}
print_awards(awards, locale = "state")
```

## Local

```{r}
print_awards(awards, locale = "local")
```

# CHAIR’S LETTER

# DEAN’S LETTER

# SAMPLE LETTER TO EVALUATORS

# BIO-SKETCHES OF INDIVIDUALS WRITING SOLICITED LETTERS OF EVALUATION and LETTERS OF EVALUATION

<!-- MRT: Although you won’t be asking for letters, this is a great time to think about who you might ask. You could list them here with a short explanation as to why. -->


# COPIES OF THE LAST FIVE ANNUAL LETTERS OF EVALUATION

# FURTHER INFORMATION

## Submitted Talks

```{r}
print_talks(dat_talks, locale = NULL, submitted = TRUE, refereed_label = NULL)
```

## Submitted Manuscripts

```{r}
dat_research <- readRDS("data/research.RDS")
pubs <- filter(dat_research, 
               str_detect(status, "accepted|in review|submitted|forthcoming"))

pubs %>%
    format_research("paper", my_bib) %>%
    remove_IN() %>%
    underline_first_author() %>%
    format_author() %>%
    print_data(prefix = "", sep = "\n\n<br />\n\n", 
               empty_message = "None\n")
```

